---
title: "ETC5513 - Assignment 2: Git Guide"
author: "Waranya Ratirotjanakul (36851256)"
date: Today
format: 
    html:
        theme: cosmo
        toc: true
        smooth-scroll: true
    typst: 
        documentclass: article
        toc: true
---

This guide demonstrates the basic steps required to create a reproducible project using RStudio and Quarto. Reproducible reporting ensures that analyses can be rerun and produce consistent results by combining code, output, and documentation in a single workflow. The purpose of this guide is to establish the foundation for version control and collaborative practices using Git and GitHub.

# Step 1 — Create a New RStudio Project and example.qmd
## 1. Create a New RStudio Project
The first step in creating a reproducible workflow is to create a new RStudio Project. A project provides a structured environment where all files related to the analysis are stored together.

To create a new project in RStudio:
1) Open RStudio.
2) Click File → New Project.
3) Select New Directory.
4) Select New Project.
5) Enter a project name (for example, gitguide_project).
6) Choose a location to save the project.
7) Click Create Project.

After completing these steps, a new folder containing an `.Rproj` file will be created.

```{r}

```

## 2. Create a Quarto File
Inside the project folder, create a simple Quarto document named `example.qmd`.

To create the file:
1) Click File → New File → Quarto Document.
2) Save the file as `example.qmd` in the project folder.

Below is a simple example of a Quarto document that can be rendered into an HTML file.

- At YMAL:

---
title: "Example Quarto Document"
format: html
---


```{r}
# Simple calculation
x <- 10
y <- 5
x + y
```

## 3. Render the Quarto File
To generate the HTML output, click the Render button in RStudio. After rendering, an HTML file named `example.html` will be created in the project folder.

When the file is rendered successfully, the output will display the result of the calculation:

10 + 5 = 15

This confirms that the Quarto document has been successfully knitted into an HTML file and demonstrates the integration of code and output within a reproducible report.

## What Your Folder Should Look Like
gitguide_project/
    example.qmd
    example.html
    gitguide_project.Rproj